Binary Latent Representations for Efficient Ranking

### 2017-06-14 paper/paper.tex
More work on related section.

\section{Related work}
\citet{shrivastava2014asymmetric} propose a solution for efficient ranking of large result sets through approximate maximum inner product search (MIPS). They extend well-known \citep{indyk1998approximate} locality-sensitive hashing techniques to the MIPS setting through asymmetric transformations of the query and candidate vectors, and show their applicability to recommender systems.

Our approach is complementary to approximate inner product search. Approximate MIPS proceeds in two stages: (1) identification of candidate result vectors through localicty-sensitive hashing, followed by (2) explicit scoring and sorting of the returned candidates. Replacing real-valued dot products by XNOR operations in the second stage will yield incremental performance gains over a real-valued MIPS approach.

\citet{Shen_2015_ICCV} expand on this approach by learning asymmetric binary hash functions. The hash functions are trained to minimize the L2 norm between the inner product matrix of the original input vectors and the inner product matrix of their binary representations. As a post-processing technique, it is a applicable to a wide range of problems. However, because the binary representations are obtained as a separate step, this approach may not be able to exploit the benefits in training a binary representation approach end-to-end.

@@

>>>>

@@

\section{Related work}
Much of existing work on efficient recommendation retrieval focuses on reducing the number of dot products that need to be performed in order to retrieve top recommendations. \citet{koenigstein2012efficient} introduces an exact branch-and-bound based on metric trees as well as an approximate algorithm that clusters users and serves recommendations computed for the cluster centers. \citet{shrivastava2014asymmetric} extend well-known \citep{indyk1998approximate} locality-sensitive hashing techniques to maximum inner product search (MIPS) through asymmetric transformations of the query and candidate vectors.

Our work complements these approaches. Binary representations are direct replacement for existing real-valued recommendations, and will serve to speed up the final predictions on the set of candidates returned from tree nodes or hash buckets.

The method that is most closely related to the model we present in this paper is \citet{Shen_2015_ICCV}, who expand on MIPS by learning asymmetric binary hash functions. The hash functions are trained to minimize the L2 norm between the inner product matrix of the original input vectors and the inner product matrix of their binary representations. As a post-processing technique, it is a applicable to a wide range of problems. However, because the binary representations are obtained as a separate step, this approach may not be able to exploit the benefits in training a binary representation approach end-to-end.
